A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-16 paper/paper.tex
Page layout mucking around
Remove the funding note for anon review, put it back in later and worry about page layout then
Last one

\title{A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work
was supported by a pile of money from a funding agency.}}
\author{The Anonymous Authors of Paper 2431 \\
Academy of Anonymous Academics, Some City, Some Country \\
anonymous@anonymous.anonymous}

@@

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:prettyheatmaps1,figure:prettyheatmaps2} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the labelled, unconnected problem instances. (Rather
than a simple scatter plot, we use darker colours to indicate a higher density
of points around a location.) We see a close correlation: we typically do
slightly less work, and sometimes do more, but instances with more than one
order of magnitude difference in search space size are rare.

>>>>

\title{A Partitioning Algorithm for Maximum Common Subgraph Problems}
\author{The Anonymous Authors of Paper 2431 \\
Academy of Anonymous Academics, Some City, Some Country \\
anonymous@anonymous.anonymous}

% \thanks{This work was supported by a pile of money from a funding agency.}

@@

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:prettyheatmaps1,figure:prettyheatmaps2} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the unlabelled and labelled, unconnected problem
instances. (Rather than a simple scatter plot, we use darker colours to
indicate a higher density of points around a location.) We see a close
correlation: we typically do slightly less work, and sometimes do more, but
instances with more than one order of magnitude difference in search space size
are rare.
